## Organizing Data

Using our synthetic data, we will discuss how to organize the data in a way that allows us to measure state transitions.

First we compile our transition database by reading in the synthetic data. 

```{r echo=TRUE, eval=TRUE}
synthetic_data <- readRDS(file = './data/icr_data.RDS')  #read the data

```

For each claim, the synthetic data includes eight features which are listed below:

* clNr: Claim Number
* LoB: Line of business
* cc: Claim Code
* AY: Accident Year
* AQ: Accident Quarter
* age: Age of the Claimant
* inj_part: Body Part Injured
* RepDel: Reporting Delay

The synthetic data includes a settlement delay for each individual claim up to a maximum of 11 years. The "Open00" through "Open11" variables with the value of "1" indicate that the claim is open at the corresponding lag and the value of "0" indicating the claim is closed at the corresponding lag. Payments for each lag are also simulated in the fields "Pay00" through "Pay11".  

To determine the transition matrices we will only need the claim number and the status and value fields ("Open00" through "Open11" and "Pay00 through Pay11"). As discussed in Section 2.1, if you were to further refine the states you could include other fields such as age of the claimant or body part injured and model the settlement lags separately based on those characteristics. 

Now that we have a better understanding of the data we are ready to manipulate the data into a format which will enable us to create the Markov transition matrices. The objective is to transform the data into a database with 12 instances for each claim number (maturities 00 through 11) with indicators for whether the claim is open or closed and whether there is value at each maturity.

We apply the states defined in Section 2.1 to our data (`oz`, `onz`, `cz`, `cnz`) in the code below.

```{r echo=TRUE, message=FALSE, warning=FALSE}
paid_data <- synthetic_data %>%  
  dplyr::select(ClNr:RepDel, dplyr::starts_with('Pay')) %>% #keep IDs and payment amounts
  tidyr::pivot_longer(cols = Pay00:Pay11, names_to = 'paid_as_of', #wide to long
    values_to = 'paid') %>% 
  dplyr::mutate(maturity = stringr::str_extract(string = paid_as_of, #extract maturity
    pattern = '[0-9]{2}')) %>%
  #calculate cumulative payments
  dplyr::group_by(ClNr) %>% mutate(cum_paid = cumsum(paid)) %>% 
  dplyr::select(-paid)
  
status_data <- synthetic_data %>%  #read the data
  dplyr::select(ClNr:RepDel, dplyr::starts_with('Open')) %>% #keep IDs and status
  tidyr::pivot_longer(cols = Open00:Open11, names_to = 'status_as_of', #wide to long
    values_to = 'status') %>% 
  dplyr::mutate(maturity = stringr::str_extract(string = status_as_of, #extract maturity
    pattern = '[0-9]{2}'))

markov_data <- dplyr::left_join(paid_data, status_data) %>% #join paid and status data
  dplyr::select(- c(paid_as_of, status_as_of, LoB, age, cc, AY, 
    AQ, inj_part, RepDel)) %>%  #remove fields not used
  dplyr::mutate(maturity = as.numeric(maturity) + 1) %>% 
  dplyr::arrange(ClNr, maturity) %>%
  dplyr::mutate(mc_status = case_when( #create Markov states decided on in Section 2.1
    cum_paid == 0 & status == 1 ~ "oz", #open zero
    cum_paid > 0 & status == 1 ~ "onz", #open non-zero
    cum_paid == 0 & status == 0 ~ "cz", #closed zero
    cum_paid > 0 & status == 0 ~ "cnz", #closed non-zero
    TRUE ~ "NA")) %>%
  dplyr::mutate(
    mc_subject = ClNr, #define variables for markovchain package
    mat_ymyp1 = maturity) %>% # maturity calculated as year minus year plus 1
  dplyr::arrange(mc_subject, mat_ymyp1) %>% 
  dplyr::ungroup()

markov_states <- c('oz', 'onz', 'cz', 'cnz') #define states

rm(paid_data, status_data, synthetic_data) #cleanup

```
The `markov_data` dataframe is now ready to be used to create our Markov transition matrices. We provide the first this data for claim number 36 to allow the reader to understand the final organization. (We selected claim number 36 as it has a reopening in interval 6 and includes several intervals where the claim is open but there are no payments.)

```{r}
markov_data %>% 
  dplyr::filter(ClNr == 36)
```
