## Developing Matrices of Observed Transitions

We now have the data organized so as to capture movements (i.e., `transitions`) between states. 

```{r echo=TRUE, message=FALSE, warning=FALSE}
transitions <- unique(markov_data$mat_ymyp1) %>% sort() #define transitions
transitions <- transitions[1:length(transitions) - 1]
transitions

```  

We use the `create_mtms` function contained in the `R` package accompanying this paper to create an `R` list object containing the incremental Markov transition matrices based on our data. 

We also present the first of the transition matrices below.
```{r echo=TRUE, message=FALSE, warning=FALSE}
mtms <- lapply(X = transitions, #all available transitions,
  create_mtms)
mtms[[1]] #to show
```  

In addition to the matrices containing the transitions between lags, we need a terminal matrix. The terminal matrix is is the is the final matrix in our development matrix.  In the terminal matrix, all claims are closed (Pr(closed -> closed) = 1, Pr (open -> closed) = 1). 

```{r echo=TRUE}
term_mat <- expand.grid(from = markov_states, to = markov_states) %>%
  dplyr::mutate(n = case_when(
    from == 'oz' & to == 'cz' ~ 1,
    from == 'onz' & to == 'cnz' ~ 1,
    from == 'cz' & to == 'cz' ~ 1,
    from == 'cnz' & to == 'cnz' ~ 1,
    TRUE ~ 0
  ))
square_term <- xtabs(n ~ from + to, data = term_mat)[c('cnz', 'cz', 'onz', 'oz'), c('cnz', 'cz', 'onz', 'oz')]

class(square_term) <- "table" 

```

We now transform these matrices from transition counts to transition probabilities and then add the terminal matrix to the end of the `list`.

```{r echo=TRUE}

mtm_selections <- lapply(mtms, function(mtm){

    mtm_prop <- (mtm %>% prop.table(margin = 1))
  
  return(mtm_prop)
})

mtm_selections[[length(mtm_selections) + 1]] <- square_term
rm(term_mat, square_term)

mtms[[1]]
mtm_selections[[1]]

```
