## Selecting Transition Probabilities

We are now ready to review these matrices and incorporate actuarial judgment into selecting transition probabilities. 


Generally, we use judgment to smooth the data or address anomalies.  In your model, you may want to eliminate the probability of a re-opening. We use the `update_mtm_selections` function from the package that accompanies this paper to adjust the transitions.

* For example, the data used to create the transition matrices may include "re-openings." For our case study we chose to keep the probability of claim re-openings and did not adjust for this outcome. 
* Another example of an instance where you would want to apply judgment is to smooth the transitions between lags. In reviewing our transition matrices, we note that in lag five to six, 60% of `oz` claims transition to `onz` and 40% stay `oz`. In the next few lags 100% of oz claims stay oz. We have selected to smooth this transition by modifying lags 6-7 and 7-8 as follows:


```{r echo=TRUE}

#Transition 6 - 7
mtm_selections[[6]] <- update_mtm_selection(mtm_selections[[6]], 
  from = 'oz', to = 'onz', selection = .4)
mtm_selections[[6]] <- update_mtm_selection(mtm_selections[[6]], 
  from = 'oz', to = 'oz', selection = .6)

#Transition 7 - 8
mtm_selections[[7]] <- update_mtm_selection(mtm_selections[[7]], 
  from = 'oz', to = 'onz', selection = .2)
mtm_selections[[7]] <- update_mtm_selection(mtm_selections[[7]], 
  from = 'oz', to = 'oz', selection = .8)

```

* We also noticed that for lag 1 `oz` transitions had a very low probability of either closing with no value or staying open with no value. We wanted to adjust for this and give claims an opportunity to either stay open zero or close zero at this early transition. 

```{r echo=TRUE}
#Transition 1 - 2
mtm_selections[[1]] <- update_mtm_selection(mtm_selections[[1]], 
  from = 'oz', to = 'cz', selection = 0.02)
mtm_selections[[1]] <- update_mtm_selection(mtm_selections[[1]], 
  from = 'oz', to = 'cnz', selection = 0.82)
mtm_selections[[1]] <- update_mtm_selection(mtm_selections[[1]], 
  from = 'oz', to = 'oz', selection = 0.04)
mtm_selections[[1]] <- update_mtm_selection(mtm_selections[[1]], 
  from = 'oz', to = 'onz', selection = .12)

```                                           
                                            
We use `plot_mtms` from the accompanying `R` package to visualize the transition matrices. The probabilities are visualized using a color gradient, the darker the blue the higher the probability of the transition. We present the observed and selected transition matrices through lag 6-7 below.


```{r echo=TRUE, fig.height=3, fig.width=5}

#plot mtms
#use length(mtms) instead of 6 if you want to print all
lapply(X = 1:6, FUN = function(x){
  print(paste('transition = ', x, 'to', x + 1))
  plot_mtm(x)
} ) %>% invisible()

```

Finally, we convert the matrices to have the `markovchain` class.

```{r echo=TRUE}
#convert the selection matrices to class = Markov Chain
mtm_selections <- lapply(mtm_selections, function(x){
  as(object = x, Class = "markovchain")
})
rm(markov_data)
```