We can now turn our attention to the development model. We create our analysis data by filtering out claims that do not develop. (We dealt with claims that do not develop in the prior section.) We also only concern ourselves with development on non-zero claims. 

```{r}
nz_dev_model <- model_data %>% 
  dplyr::filter(ultimate > cum_paid) %>% 
  dplyr::filter(cum_paid > 0)

nz_closing_lags <-  unique(nz_dev_model$lag_to_close) %>% sort()


```

Now we perform exploratory data analysis. We present cloisng lags 2 and 7 below.

```{r}
par(mfrow = c(1, 2))

lapply(X = c(2, 7), FUN = function(closing_lag){
  
  plot_data <- nz_dev_model %>% 
    dplyr::filter(lag_to_close == closing_lag) #for loop
  
  
  plot(x = log(plot_data$cum_paid), xlab = 'log(claims_paid)',
    y = log(plot_data$ultimate), ylab = 'log(setttelement value)',
    main = paste('Closing Lag = ', closing_lag))
  
  lines(x = plot_data$cum_paid, y = plot_data$cum_paid, col = 'red')
  
}) %>% invisible()
```

Our principal observation is that the the variance of the errors seems to increase with the mean until we (approximately) reach a paid value of `exp(10)` (`r scales::comma(exp(10))`). We therefore elect to fit a `glm` with a gamma error distribution to claims with initial value less than `r scales::comma(exp(10))` and a separate linear model to claims greater than `r scales::comma(exp(10))`.

For brevity, we will only present the model for closing lag 2.

```{r}
plot_data <- nz_dev_model %>% 
  dplyr::filter(lag_to_close == 2)  

plot(x = log(plot_data$cum_paid), xlab = 'log(claims_paid)',
  y = log(plot_data$ultimate), ylab = 'log(setttelement value)',
  main = paste('Closing Lag = ', 2))

lines(x = log(plot_data$cum_paid), y = log(plot_data$cum_paid), col = 'red')
abline(v = 10, col = 'red')

sev_model_lt10 <- glm(formula = log(ultimate) ~ log(cum_paid),
  data = plot_data, family = Gamma(link = 'identity'), 
  subset = log(cum_paid) < 10)

points(x = log(plot_data$cum_paid)[log(plot_data$cum_paid) < 10], 
  y = predict(object = sev_model_lt10), col = 'blue', type = 'l')

sev_model_gt10 <- lm(formula = log(ultimate) ~ log(cum_paid),
  data = plot_data, subset = log(cum_paid) >= 10)

points(x = log(plot_data$cum_paid)[log(plot_data$cum_paid) >= 10], 
  y = predict(object = sev_model_gt10), col = 'green', type = 'l')

rm(plot_data)
```

```{r}
nz_lt_10 <- lapply(X = nz_closing_lags, FUN = function(closing_lag){
  
  model_data <- nz_dev_model %>% 
    dplyr::filter(lag_to_close == closing_lag)  
  
  sev_model_lt10 <- glm(formula = log(ultimate) ~ log(cum_paid),
    data = model_data, family = Gamma(link = 'identity'), 
    subset = log(cum_paid) < 10)
}) %>% invisible()

severity_model_df$nz_lt_10 <- nz_lt_10


nz_gt_10 <- lapply(X = nz_closing_lags, FUN = function(closing_lag){
  
  model_data <- nz_dev_model %>% 
    dplyr::filter(lag_to_close == closing_lag)  
  
  lm(formula = log(ultimate) ~ log(cum_paid),
    data = model_data, subset = log(cum_paid) >= 10)
  
}) %>% invisible()

severity_model_df$nz_gt_10 <- nz_gt_10
rm(sev_model_gt10, sev_model_lt10, nz_dev_model, nz_gt_10, nz_lt_10)
```


