# Applying the Model

We now have all the component models to develop our estimates. We start by generating test data. We use the same approach as we used to generate the model used to parameterize the model with the exception of the simulation seed.

We then "cutoff" the data so that we only have information through a particular valuation date. (We use the same code presented in Section 2.2 except to applying an additional filter to exclude any observations valued after year-end 2005).

```{r echo=FALSE}
#test_data <- readRDS(file = './data/icr_data.RDS')
#test_data <- readRDS(file = './data/test_data.RDS')

test_data <- dplyr::left_join(
  
  readRDS(file = './data/icr_data.RDS') %>% 
    dplyr::select(ClNr:RepDel, dplyr::starts_with('Pay')) %>% #keep IDs and payment amounts
    tidyr::pivot_longer(cols = Pay00:Pay11, names_to = 'paid_as_of', #wide to long
      values_to = 'paid') %>% 
    dplyr::mutate(maturity = stringr::str_extract(string = paid_as_of, #extract maturity
      pattern = '[0-9]{2}')) %>%
    dplyr::mutate(maturity = as.numeric(maturity) + 1) %>% 
    mutate(cal_year = AY + maturity - 1) %>% 
    #calculate cumulative payments
    dplyr::group_by(ClNr, AY) %>% 
    mutate(cum_paid = cumsum(paid)),
  
  readRDS(file = './data/icr_data.RDS') %>% 
    dplyr::select(ClNr:RepDel, dplyr::starts_with('Open')) %>% #keep IDs and payment amounts
    tidyr::pivot_longer(cols = Open00:Open11, names_to = 'open_as_of', #wide to long
      values_to = 'status') %>% 
    dplyr::mutate(maturity = stringr::str_extract(string = open_as_of, #extract maturity
      pattern = '[0-9]{2}')) %>%
    dplyr::mutate(maturity = as.numeric(maturity) + 1) %>% 
    mutate(cal_year = AY + maturity - 1) %>% 
    dplyr::mutate(status_year = status * cal_year) %>% 
    #calculate cumulative payments
    dplyr::group_by(ClNr, AY) %>% 
    mutate(last_open = max(status_year)) %>% 
    dplyr::select(-status_year)
)
```
We present the familiar data triangle below.
```{r triangle}
#table(test_data$AY[test_data$cal_year], test_data_2005$maturity)
```

The following table presents the number of open (`status == 1`) and closed (`status == 0`) claims at the current valuation (year-end 2005).

```{r}
#val_2005 <- test_data_2005 %>% 
#  dplyr::filter(val_year == 2005)
#table(val_2005$AY, val_2005$status)
```

We now create the dataset for the simulation model.

```{r echo=TRUE}
val_date <- 2005

settle_sim_test <- test_data %>% 
  dplyr::filter(cal_year == val_date) %>% 
  dplyr::mutate(mtm_code = case_when(
    status == 1 & cum_paid == 0 ~ "oz",
    status == 1 & cum_paid > 0 ~ "onz",
    status == 0 & cum_paid == 0 ~ "cz",
    status == 0 & cum_paid > 0 ~ "cnz",)) %>% #assign mtm_code
  dplyr::mutate(
    mtm_code_with_mat = paste(mtm_code, maturity, sep = '_'))
```

We use the function `open_sim` from the accompanying `R` package. For our case study we run 100 iterations (to keep computing time reasonable) for each claim. There are two inputs to the `open_sim` function, the first is the identifier for each claim in the database of open claims, in this case study that is the `ClNr` field of our `open_claims` database. The next input for the function is the last maturity of the transition matrix which in this case study is 12. 

```{r echo=TRUE, message=FALSE, warning=FALSE}
set.seed(14159) #for reproducibility
my_iters = 100
last_mat = 12 #last maturity
sim_claims <- settle_sim_test
state_sims <- lapply(X = sim_claims$ClNr, FUN = claims_simulation, last_mat)
names(state_sims) <- paste0('claim_', sim_claims$ClNr)

rm(last_mat, sim_claims)
#rm(mtm_selections)
```

After running the simulation we produce a `list` of each open claim and the 100 iterations of the closing states. Having the ability to view the simulation this closely allows you to drill down into each individual claim which is a resourceful tool when explaining results.

