The final step is to append the severity values to each data frame

```{r functions}
extract_no_add_pay_rate <- function(df){
    #df <- test_claim #testing
  sapply(X = 1:nrow(df), FUN = function(row_no){
    #row_no <- 9 #testing
    cum_pd <- df$cum_paid[row_no] #cum_pd
    car_df <- df$no_add_pay[row_no][[1]] #car_df
    car_pr <- car_df$no_add_pay_rate[sum(cum_pd > car_df$layer_start)]
    if(is.null(car_pr)) car_pr <- 1
    return(car_pr)
  }, simplify = TRUE) %>% unlist()
}

sim_sev <- function(cum_paid, lt10_model, gt10_model, z_model) {
  
  my_newdata <- data.frame('cum_paid' = cum_paid)
  
  my_predicted <- predict.glm(object = lt10_model, newdata = my_newdata)
  shape <- MASS::gamma.shape(lt10_model)$alpha
  sim_lt10 <- rgamma(n = 1, shape = shape, rate = shape/my_predicted) %>% exp()
  
  #gt10_model <- test_claim$nz_gt_10[[13]]
  my_sd_log <- summary(gt10_model)$sigma
  if(is.nan(my_sd_log)) my_sd_log <- 0
  sim_gt10 <- rlnorm(n = 1, meanlog = predict.lm(object = gt10_model, 
    newdata = my_newdata), sdlog = summary(gt10_model)$sigma)
  
  #z_model <- test_claim$z_dev[[1]]
  z_sim <- sample(z_model, size = 1) %>% exp()
  
  val_to_return <- dplyr::case_when(
    cum_paid == 0 ~ z_sim,
    cum_paid > 0 & cum_paid < exp(10) ~ sim_lt10,
    cum_paid >= exp(10) ~ sim_gt10)
  
  return(val_to_return)
}

```

In the code below, we follow the following recipe in simulating severity values.

* For each claim, we first retain only those fields that we will need.
* We then `join` our severity model dataframe. This step adds dataframe columns.
* Recall that the model for no additional payments required a lookup from a dataframe of empirical values. We use the `extract_no_add_pay_rate` function to perform that lookup. If a closed claim does not reopen, we assign a 100% probability on no new claims. We then sample from a uniform distribution to model additional payments.
* We feed the various component models and the paid value into the `sim_sev` function. That function returns the severity value resulting from the applicable severity model. We then only use that value if the claim has simulated as having additional payment.


```{r message=FALSE, warning=FALSE}
#attach Severity Model
full_sim_model <- lapply(X = state_sims, FUN = function(settle_sim) {
  
  cum_paid <- settle_sim$cum_paid
  
  settle_sim$full_sim <- settle_sim$settle_lag %>% 
    dplyr::rename(lag_to_close = settle_lag) %>% 
    dplyr::left_join(severity_model_df)
  
  
  return(settle_sim)
  
}) 


#add the no pay probabilities


full_sim_model <- lapply(X = full_sim_model, FUN = function(claim){
  
  cum_paid <- claim$cum_paid
  my_df <- claim$full_sim
  
  no_add_pays <- sapply(X = 1:nrow(my_df), FUN = function(row_no){
    
    lag_to_close <- my_df$lag_to_close[row_no]
    
    no_add_pay <- if(lag_to_close != 0) {
      car_df <-  my_df$no_add_pay[[row_no]]
      car_df$no_add_pay_rate[sum(cum_paid >= car_df$layer_start)]
    } else {
      1
    }
    
    
  }, simplify = TRUE) 
  
  my_df$no_add_pay_pr <- no_add_pays
  my_df$add_pay_sim <- runif(n = my_iters)
  my_df$add_pay <- my_df$add_pay_sim > my_df$no_add_pay_pr
  
  
  claim$full_sim <- my_df
  
  return(claim)
  
}) %>% invisible()

#now the severity values

full_sim_model <- lapply(X = full_sim_model, FUN = function(claim){
  
  cum_paid <- claim$cum_paid
  my_df <- claim$full_sim
  my_newdata <- data.frame('cum_paid' = cum_paid)
 
  ultimates <- sapply(X = 1:nrow(my_df), FUN = function(row_no){
    
    if(my_df$add_pay[[row_no]]) {
      
      #less than exp(10)
      lt10_mod <- my_df$nz_lt_10[[row_no]]
      my_predicted <- predict.glm(object = lt10_mod, newdata = my_newdata)
      shape <- MASS::gamma.shape(lt10_mod)$alpha
      ult_lt10 <- rgamma(n = 1, shape = shape, rate = shape/my_predicted) %>% exp()
      
      #greater than exp(10)
      gt10_mod <- my_df$nz_gt_10[[row_no]]
      my_sd_log <- summary(gt10_mod)$sigma
      if(is.nan(my_sd_log)) my_sd_log <- 0
      ult_gt10 <- rlnorm(n = 1, meanlog = predict.lm(object = gt10_mod, 
        newdata = my_newdata), sdlog = my_sd_log)
      
      #zeros
      
      ult_z <- sample(my_df$z_dev[[row_no]], size = 1) %>% exp()
      
      dplyr::case_when(
        exp(cum_paid) > 10 ~ ult_gt10,
        cum_paid == 0 ~ ult_z,
        exp(cum_paid) <= 10 ~ ult_gt10,
      )
      
      
    } else {
      return(cum_paid)
    }
    
    
  }, simplify = TRUE) 
  
  my_df$ultimate <- pmax(cum_paid, ultimates)
  
  claim$full_sim <- my_df
  
  return(claim)
  
    
}) %>% invisible()
```  


```{r warning=FALSE}
results_list <- lapply(X = full_sim_model, function(x) x$full_sim)
results_df <- dplyr::bind_rows(results_list) %>% 
  dplyr::select(iteration, ClNr, AY, cum_paid, ultimate) 
```


```{r}
actual <- dplyr::left_join(
  #paid at 2005
  test_data %>% 
  dplyr::filter(maturity == 12) %>%
  dplyr::select(ClNr, AY, ultimate = cum_paid),
  
  #ultimate
  test_data %>% 
  dplyr::filter(cal_year == 2005) %>% 
  dplyr::select(ClNr, AY, paid_2005 = cum_paid)
  ) %>% 
  dplyr::group_by(AY) %>% 
  dplyr::summarise(paid_2005 = sum(paid_2005), ultimate = sum(ultimate), 
    count = n()) %>% 
  dplyr::mutate(avg_sev = ultimate / count)

actual
```

```{r}
model_result <- results_df %>% 
  dplyr::group_by(AY) %>% 
  dplyr::summarise(sim_ult = sum(ultimate) / 10)
```

```{r fig.height=3, fig.width=3}
lapply(X = 1995:2005, FUN = function(ay){
  results_df %>% 
    dplyr::filter(AY == ay) %>% 
    dplyr::group_by(iteration) %>% 
    dplyr::summarise(sim_ult = sum(ultimate)) %>% 
    dplyr::pull(sim_ult) %>% 
    hist(main = ay)
  
  abline(v = actual$ultimate[actual$AY == ay], col = 'red')
  abline(v = actual$paid_2005[actual$AY == ay], col = 'blue')
}) %>% invisible()
```




